Compositional Quantitative Resource Analysis of C Programs

### 2014-06-21 paper/main.tex
adding more references

Notable tools that have been developed include Speed [XXX], KoAT
[XXX], Pubs [XXX], RANK [XXX], and LOOPUS [XXX].

@@

  abstract interpretation based invariant generation [XXX speed] or
  translation of the program into a term-rewriting system [costa,
  tacas] without providing \emph{verifiable certificates} for the
  correctness of the derived bound.

@@

Don Knuth correctly points out in a recent interview [XXX] that the
state-of-the-art in formal quantitative methods still falls short
in comparison with semantic techniques [xxx].

@@

    -- Donald Knuth, 2014

>>>>

Notable tools that have been developed include
SPEED~\cite{GulwaniMC09}, KoAT~\cite{BrockschmidtEFFG14},
PUBS~\cite{AlbertAGPZ12}, Rank~\cite{AliasDFG10}, and LOOPUS~\cite{SinnZV14}.

@@

  abstract interpretation based invariant
  generation~\cite{GulwaniMC09} or translation of the program into a
  term-rewriting system~\cite{BrockschmidtEFFG14, SinnZV14} without
  providing \emph{verifiable certificates} for the correctness of the
  derived bound.

@@

Knuth correctly points out in a recent interview~\cite{KnuthInter}
that the state-of-the-art in formal quantitative methods still falls
short in comparison with semantic techniques.

@@

    -- Donald E. Knuth, 2014
